The Analysis of Pluralistic Ignorance of Married Men in Saudi Arabia on Women Working Outside of Home (WWOH) ^[Code and data are available at: https://github.com/YcartXin/Analysis-of-Men-in-Saudi-Arabia-on-WWOH; Reproduction DOI: https://doi.org/10.48152/ssrp-1wa4-dk30]

### 2024-02-15 paper/paper.qmd
Deleted unwanted data from the main experiment data set and created new graphs.

---
title: "The Analysis of Pluralistic Ignorance of Married Men in Saudi Arabia on Women Working Outside of Home (WWOH) ^[Code and data are available at: https://github.com/YcartXin/Analysis-of-Men-in-Saudi-Arabia-on-WWOH]"
author: 
  - Tracy Yang
  - Alex Sun
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: 
  typst:
    toc: true
number-sections: true
bibliography: references.bib
---

@@

Lastly, the data set "Follow Up Clean" is information from the follow up survey that was conducted on the same sample as the main experiment three months alter. This survey is a phone call and the variables that will be used is to examine the change in the participants' wifes' employment since the main experiment. This data set contains 500 observations and 33 variables.

## Exploring the data {#sec-explore}
After the data cleaning process, irrelevant variables were removed along with empty responses. The online survey data now consists of only one variable with 728 observations. The variable signifies whether the respondent supports women working outside of home.

@tbl-sampleonline shows what the online national survey data looks like after cleaning.

```{r}
#| echo: false
#| label: tbl-sampleonline
#| tbl-cap: Sample of Cleaned Online National Survey Data of Saudi Arabian Men on WWOH
online_cleaned |> slice(1:5) |> kable()

@@

# Results {#sec-results}
This section will first affirm the findings in the original paper with the cleaned data. As stated in @sec-intro, the three main claims made by Bursztyn et.al are:
+ The vast majority of married men in Saudi Arabia privately support WWOH.
+ The married men massively underestimate the level of support from other men in their communities.
+ Correcting these beliefs about others’ feelings will affect the outcome of whether the married man's wife work.

@@

Starting from the second claim, we will be using the main experiment data. Before manipulating it into graphs and tables, we can first understand the cleaned data better with summary statistics.

@@

The last claim this replication paper is going to focus on is that correcting beliefs about others' feelings will affect the outcome of whether the married man's wife works. In the main experiment done by Bursztyn et.al, a follow up survey three months later records the difference in the participant's wife's employment difference @paper. As the men experienced learning about others' surprisingly supportive views on WWOH during the first survey, this three-month difference in wifes' employments maybe attributed to the correcting of beliefs. The difference is shown in  below.

@@

```
As seen in @tbl-empl, there are slight differences between the treatment and control group in terms of the participants' wives employment since the first survey.

>>>>

---
title: "The Analysis of Pluralistic Ignorance of Married Men in Saudi Arabia on Women Working Outside of Home (WWOH) ^[Code and data are available at: https://github.com/YcartXin/Analysis-of-Men-in-Saudi-Arabia-on-WWOH; Reproduction DOI: https://doi.org/10.48152/ssrp-1wa4-dk30]"
author: 
  - Tracy Yang
  - Alex Sun
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: 
  typst:
    toc: true
number-sections: true
bibliography: references.bib
---

@@

Lastly, the data set "Follow Up Clean" is information from the follow up survey that was conducted on the same sample as the main experiment three months alter. This survey is a phone call and the variables that will be used is to examine the change in the participants' wifes' employment since the main experiment as well as whether the husband was in the treatment or control group. This data set contains 500 observations and 33 variables.

## Exploring the data {#sec-explore}
After the data cleaning process, irrelevant variables were removed along with empty responses. The online survey data now consists of only one variable with 728 observations. The variable "c_outside_self" signifies whether the respondent supports women working outside of home. The follow up data now consists of 361 observations with three variables: "emply_prev", "emply_now", "condition2". The second main experiment data includes 702 observations and 1 variable as well, which is the frequency of discussion of WWOH issues.

@@

# Results {#sec-results}

## Aanalysing origial paper
This section will try to affirm the findings in the original paper with the cleaned data. As stated in @sec-intro, the three main claims made by Bursztyn et.al are:
+ The vast majority of married men in Saudi Arabia privately support WWOH.
+ The married men massively underestimate the level of support from other men in their communities.
+ Correcting these beliefs about others’ feelings will affect the outcome of whether the married man's wife work.

@@

Starting from the second claim, we will be using the main experiment data. Before manipulating it into graphs and tables, we can first understand the cleaned data better with summary statistics. The "condition2" variable separates the treatment and control groups.

@@

The last claim this replication paper is going to focus on is that correcting beliefs about others' feelings will affect the outcome of whether the married man's wife works. In the main experiment done by Bursztyn et.al, a follow up survey three months later records the difference in the participant's wife's employment difference @paper. As the men experienced learning about others' surprisingly supportive views on WWOH during the first survey, this three-month difference in wifes' employments maybe attributed to the correcting of beliefs. The difference is shown in @tbl-empl below.

@@

```
As seen in @tbl-empl, there are slight differences between the treatment and control groups in terms of the participants' wives employment since the first survey. The number of women who moved from not working three months ago to now working is four in the treatment group while only 1 in the control group. The number of women who were employed but is not now is 4 is the treatment group and 3 in the control group. Due to the limited data size of around 350 and the insignificant differences in the changes in employment between the treatment and control group, this @tbl-empl cannot be decisive evidence in supporting correcting beliefs about others' feelings will affect the outcome of whether the married man's wife works. However, the tables fall more in favour of agreeing than disagreeing.

## Further Analysis
In this section, the analysis will branch off from the original paper and explore the demographics of the men who support/oppose women working outside of home. We will first consider education as a factor that may determine support for WWOH. Research shows that one additional year of education reduces the probability of agreeing with women's traditional gender role @educ. This relationship in the existing data is explored in XX.

```{r}
#| echo: false
#| label: fig-educ
#| fig-cap: Graph on the impact of education on supporting WWOH

main_cleaned <- mainexp_raw_data |> clean_names() |> 
  na.omit(age)|> mutate(
  age_groups = case_when(
  age <= 23 ~ 1,
  age >= 30 ~ 3,
  TRUE ~ 2)) |> filter(married == 1)

eduimpact <- main_cleaned |> mutate(support = ifelse(
  outside_self == 1, "support", "oppose")) |>
  mutate(edu_words = case_when(

  ))

eduimpact |>
  ggplot(mapping = aes(x = education, fill = support)) +
  geom_bar() +
  labs(x = "Age group", y = "Number of observations", fill = "Vote") +
  theme(legend.position = "bottom")
